\beginsong{Otherside}[by={Red Hot Chilli Peppers}]


% http://bettyloumusic.com/otherside.htm

\beginchorus
\[Am]How long, how l\[F]ong will I \[C]slide
S\[G]parate my \[Am]si\[F]de, I \[C]don't,
I \[G]don't believe it's \[Am]ba\[F]d
Slit my throat, it's \[G]all I ever.
\endchorus

\beginverse
\[Am] I heard your voice through a \[Em]photograph,
\[Am] I thought it up, it brought \[Em]up the past.
\[Am] Once you know you can \[Em]never go back,
I've got to \[G]take it on the \[Am]otherside.
\endverse

\beginverse
^ Centuries are what it ^meant to me,
^ a cemetery where I ^marry the sea,
^ stranger things could never ^change my mind,
I've got to ^take it on the ^otherside.
\[G]Take it on the \[Am]otherside,
\[G]take it on, \[Am]take it on.
\endverse

\textnote{Refrain}

\beginverse
^ Pour my life into a ^paper cup,
^ the ashtray's full and I'm ^spillin' my guts.
^ She wants to know am I ^still a slut,
I've got to ^take it on the ^other side.
\endverse

\beginverse
^ A scarlet starlet and she's ^in my bed,
^ a candidate for my ^soul mate bled,
^ pull the trigger and ^pull the thread,
I've got to ^take it on the other ^side.
\[G]Take it on the \[Am]otherside,
\[G]take it on, \[Am]take it on.
\endverse

\textnote{Refrain}

\beginverse
\[E] Turn me on, take me for a hard ride,
\[C] burn me out, leave me on the other side.
\[E] I yell and tell it that it's not my friend,
I tear it \[C]down I tear it down, and then it's born again.

\[Am] \[F] \[C] \[G]
\endverse

\textnote{Refrain}

\endsong